---
title: "IE425project"
author: ' SEYMA CAKIR'
date: "30 06 2021"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```



# PROJECT REPORT 
## Bogazici University
## Necati Aras, IE 425 

**Import Data** 


```{r, warning=FALSE}
library(lubridate)
library(data.table)
library(dplyr)
library(forecast)
#install.packages("caret", dependencies = TRUE)
library(caret)
library(writexl)



train <- read.csv("C:/Users/seyma/Desktop/IE425project/kobe-train.csv", header = TRUE,sep = ",")
test <- read.csv("C:/Users/seyma/Desktop/IE425project/kobe-test.csv", header = TRUE,sep = ",")
submission <- read.csv("C:/Users/seyma/Desktop/IE425project/kobe-sample-submission.csv", header = TRUE,sep = ",")


```

  First of all, the structure of data is examined and the variable which  are catergaric is converted to factor variable, and the game_date data refers to date of game, therefore, It conversted firstly  as a date and since there is too much date to evalute as categoric it is converted to numeric variable to show the shot accuracy dependicies with during the time. 



```{r}

summary(train)
str(train)
train$shot_made_flag  <- factor(train$shot_made_flag )
train$action_type <- factor(train$action_type)
train$combined_shot_type <-factor(train$combined_shot_type)
train$game_id <- factor(train$game_id)
train$game_event_id <- factor(train$game_event_id)
train$playoffs <- factor(train$playoffs)
train$shot_type  <- factor(train$shot_type)
train$shot_zone_area  <- factor(train$shot_zone_area)
train$shot_zone_basic  <- factor(train$shot_zone_basic)
train$shot_zone_range   <- factor(train$shot_zone_range)
train$team_id     <- factor(train$team_id)
train$team_name  <- factor(train$team_name) 
train$game_date   <- as.Date(train$game_date, format= "%d.%m.%Y") 
train$game_date <- as.numeric(train$game_date)
train$matchup    <-  factor(train$matchup)
train$opponent <- factor(train$opponent)

test$action_type <- factor(test$action_type)
test$combined_shot_type <-factor(test$combined_shot_type)
test$game_id <- factor(test$game_id)
test$game_event_id <- factor(test$game_event_id)
test$playoffs <- factor(test$playoffs)
test$shot_type  <- factor(test$shot_type)
test$shot_zone_area  <- factor(test$shot_zone_area)
test$shot_zone_basic  <- factor(test$shot_zone_basic)
test$shot_zone_range   <- factor(test$shot_zone_range)
test$team_id     <- factor(test$team_id)
test$team_name  <- factor(test$team_name) 
test$game_date   <- as.Date(test$game_date, format= "%d.%m.%Y") 
test$game_date <- as.numeric(test$game_date)
test$matchup    <-  factor(test$matchup)
test$opponent <- factor(test$opponent)

 
```


### Data Dictionary

action_type: Different shot types (total 57)

combined_shot_type: General shot types (total 6)

game_event_id: Unique id to identify each game (1558 for train set)

lat: latitude of the stadium

lon: longitude of the stadium

loc_x: x-axis location from where the shot was taken (-250 = right bottom to 250 = right top when basket is in right center)

loc_y: y-axis location from where the shot was taken (-40 = right side to 900 = left side when basket is in right center)

minutes_remaining: minutes remaining in a period (max 12)

period and  playoffs: period of play (in general there are 4 but in case of ties it can extend, in this case till 7)

season: NBA Season (1996-97 to 2015-16)

seconds_remaining: seconds remaining in a period

shot_distance: distance (in meters) from where the shot was taken

shot_type: 2Pt or 3Pt

shot_zone_area: Basketball Area from where the shot was taken (BC, C, LC, L, RC, R)

shot_zone_basic: Basketball Zone from where the shot was taken (Total 7)

shot_zone_range: Range (in meters) from where the shot was taken (<8, 8-16, 16-24, 24+, Back Court)

team_id: Always same (LA -> id)

team_name: Always same (LA)

game_date: Date at which the game was played

matchup and  opponent: Opponent Team and Matchups 

shot_made_flag: If the shot was a hit or a miss (Dependent Variable)


the dictionary of data taken from [Akshay Kher's Kaggle Account](https://www.kaggle.com/c/kobe-bryant-shot-selection/discussion/20888)





```{r}

ggplot(train, aes(x=factor(shot_made_flag)))+
  geom_bar(stat="count", width=0.7)+
  labs(
    x = "made_shot_flag",
    main = "the distribution of Kobe  Bryant Shots"
  )+
  theme_minimal()





```


To get more simplex model and reduce complexity of model, I will try eliminate some attributes.

```{r}
summary(train)
```


**the variables do not have particular difference**

Since, Kobe Bryant only plays in LAL during his career, I exclude team_id and team_name.


Since, the matcups  refers to which team opponet of LAL, I also exclude matchups.
- the reason of matchups eliminated instead of opponent, the matchups make more complex models since it has also information which team is host.



**The time dependent variables**

game_id is determined by game_date and opponents,it is unique as much as game_date, I exclude game_id.

the game_event_id is very depend on time remaining and period and it has many category which makes models too complex I also exclude it. 



**the distance depended variables:** 

And, shot_zone_area, shot_zone_range, shot_zone_basic and shot_type variables is determined by location x, location y, and distance. 

lag and lon variables very standart and changes in small, I think the accuracy of shots more dependent to distance between target not the size of target area. 
therefore, I also exclude them. 

```{r, out.width= '50%'}


 ggplot(train, aes(x=loc_x, y=loc_y)) +
  geom_point(aes(color=shot_made_flag), alpha= 0.25) +
  labs(title="SHOTS BY X-Y ") +
  theme_minimal() +
  theme(legend.position="left",
        plot.title=element_text(hjust=0.5)) 

 ggplot(train, aes(x= shot_distance, y=shot_made_flag)) +
  geom_point(aes(color=shot_made_flag), alpha= 0.25) +
  labs(title="SHOTS BY DISTANCE ") +
  theme_minimal() +
  theme(legend.position="left",
        plot.title=element_text(hjust=0.5)) 

```





```{r, include=FALSE,out.width='50%' }


ggplot(train, aes(x=lon, y=lat)) +
  geom_point(aes(color=shot_zone_range)) +
  labs(title="Shot Zone Range") +
  theme_minimal() +
  theme(legend.position="left",
        plot.title=element_text(hjust=0.5)) 


ggplot(train, aes(x=lon, y=lat)) +
  geom_point(aes(color=shot_zone_basic)) +
  labs(title="Shot Zone Basic") +
  theme_minimal() +
  theme(legend.position="left",
        plot.title=element_text(hjust=0.5)) 
 
ggplot(train, aes(x=lon, y=lat)) +
  geom_point(aes(color=shot_zone_area)) +
  labs(title="Shot Zone Area") +
  theme_minimal() +
  theme(legend.position="left",
        plot.title=element_text(hjust=0.5)) 
 
ggplot(train, aes(x=lon, y=lat)) +
  geom_point(aes(color= shot_type)) +
  labs(title="Shot Type") +
  theme_minimal() +
  theme(legend.position="left",
        plot.title=element_text(hjust=0.5)) 

```

```{r}
df <- train[,c("shot_made_flag","action_type","combined_shot_type", "loc_x", "loc_y","minutes_remaining","game_date", "period", "playoffs", "season", "seconds_remaining", "shot_distance", "opponent")]
test <- test[,c("X","action_type","combined_shot_type", "loc_x", "loc_y","minutes_remaining","game_date", "period", "playoffs", "season", "seconds_remaining", "shot_distance", "opponent")]
names(test) <- c("shot_made_flag","action_type","combined_shot_type", "loc_x", "loc_y","minutes_remaining","game_date", "period", "playoffs", "season", "seconds_remaining", "shot_distance", "opponent")



```





## Models 

To prevent randomness in models in every run,  I use set.seed() function


```{r}
set.seed(425)
```



### GLM model 


I use cross validation technique 



```{r, eval=FALSE}

control=trainControl(method='repeatedcv',number=10,repeats=5)
glm <- train(shot_made_flag~., data=df, method="glm", metric="Accuracy",trControl = control)
summary(glm)
confusionMatrix(glm)
varImp(glm)


```


Null deviance: 31792  on 23126  degrees of freedom


Residual deviance: 28064  on 23013  degrees of freedom


AIC: 28292


Number of Fisher Scoring iterations: 12

**glm variable importance**


only 20 most important variables shown (out of 113)


action_typeJump Shot                     100.00

action_typeLayup Shot                    92.79

action_typeTip Shot`                     91.69

action_typeHook Shot`                    88.78

action_typeFadeaway Jump Shot            72.65

action_typeTurnaround Jump Shot          71.87

action_typeFinger Roll Shot               66.93

action_typeTurnaround Fadeaway shot      66.81

period                                   64.64

action_typeDriving Jump shot             64.62

action_typeReverse Layup Shot            64.60

minutes_remaining                        63.49

seconds_remaining                        62.91

action_typeStep Back Jump shot           62.81

action_typeRunning Jump Shot              55.65

action_typeDriving Layup Shot             54.16
action_typePullup Jump shot               53.88

action_typeAlley Oop Layup shot           53.60   

action_typeFloating Jump shot             53.31

action_typeRunning Layup Shot             50.84



**Cross-Validated (10 fold, repeated 5 times) Confusion Matrix**

(entries are percentual average cell counts across resamples)

*************Actual

Prediction   0    1 

**********0 47.6  24.

**********1 7.8  20.5
             
 

         
                           
 Accuracy (average) : 0.681



### rpart model 


```{r, eval=FALSE}

rpart_mod = train(
  shot_made_flag ~ .,
  data = df,
  method = "rpart",
  trControl = control,
  metric= "Accuracy",
  tuneGrid = expand.grid(cp = c(1:100)*0.01)
)

rpart_mod
confusionMatrix(rpart_mod)
varImp(rpart_mod)

```

CART 

23127 samples

12 predictor

2 classes: '0', '1' 

No pre-processing

Resampling: Cross-Validated (10 fold, repeated 5 times) 

Summary of sample sizes: 20815, 20814, 20814, 20814, 20815, 20815, ... 

Resampling results across tuning parameters:

cp     Accuracy   Kappa    

0.001  0.6795172  0.32921447

0.002  0.6785833  0.3277267

0.003  0.6783844  0.3277424

0.004  0.6783844  0.3277424

0.005  0.6783844  0.3277424

0.006  0.6783844  0.3277424

0.007  0.6783844  0.3277424

0.008  0.6783844  0.3277424

0.009  0.6783844  0.3277424

0.010  0.6783844  0.3277424


Accuracy was used to select the optimal model using the largest value.

The final value used for the model was cp = 0.001.

**Cross-Validated (10 fold, repeated 5 times) Confusion Matrix**

(entries are percentual average cell counts across resamples)

********** Actual 

Prediction    0    1

*********0 47.0 23.6

*********1  8.4 21.0

Accuracy (average) : 0.6795

**rpart variable importance**

only 20 most important variables shown (out of 129)


action_typeJump Shot          100.0000

combined_shot_typeDunk         74.2333

combined_shot_typeJump Shot    48.6160

shot_distance                  47.1314

action_typeLayup Shot          31.3255

action_typeDriving Layup Shot  27.9414

action_typeSlam Dunk Shot      11.6487

combined_shot_typeLayup         9.8157

action_typeDriving Dunk Shot    5.3397

game_date                       4.1191

loc_y                           3.9863

combined_shot_typeTip Shot      2.8608

action_typeTip Shot             2.7956

loc_x                           1.1062

minutes_remaining               0.6360

season2002-03                   0.5499

season2011-12                   0.5140

seconds_remaining               0.3258

season2014-15                   0.1825

opponentDEN                     0.1628














### Random Forest Model 


```{r, eval=FALSE}
control3 <- trainControl(method='cv',number=10)
mtry <- c(1:12)

rftree1 <- train(shot_made_flag~., data=df, method = "rf", metric = 'Accuracy',trControl = control3, ntree = 100,  tuneGrid = expand.grid(.mtry = mtry))
rftree1
confusionMatrix(rftree1)
varImp(rftree1)

```


Random Forest 

23127 samples

12 predictor

2 classes: '0', '1' 

No pre-processing

Resampling: Cross-Validated (10 fold) 

Summary of sample sizes: 20814, 20814, 20814, 20814, 20815, 20814, ... 

Resampling results across tuning parameters:



mtry  Accuracy   Kappa      

1    0.5554977  0.004283448

2    0.6245946  0.194993294

3    0.6720707  0.307521928

4    0.6810648  0.330586192

5    0.6806324  0.330171076

6    0.6817134  0.332212717

7    0.6809351  0.330372175

8    0.6803729  0.328966535

9    0.6802863  0.328715516

10    0.6794215  0.327008566

11    0.6784268  0.325311178

12    0.6765679  0.322031223


Accuracy was used to select the optimal model using the largest value.

The final value used for the model was mtry = 6.


**ConfusionMatrix**
  
********** actual

Prediction     0    1

**********0   47.6 24.1

**********1    7.8 20.5

Accuracy (average) : 0.6817


**rf variable importance**


only 20 most important variables shown (out of 118)


action_typeJump Shot            100.000

shot_distance                    50.439

game_date                        49.817

loc_y                            49.112

loc_x                            45.929

seconds_remaining                43.308

combined_shot_typeDunk           41.660

action_typeLayup Shot            31.903

minutes_remaining                30.474

combined_shot_typeJump Shot      28.643

action_typeRunning Jump Shot     20.505

action_typeDriving Layup Shot    20.206

period                           18.959

combined_shot_typeLayup          14.471

action_typeSlam Dunk Shot         9.298

action_typeJump Bank Shot         8.543

action_typePullup Jump shot       8.447

action_typeTurnaround Jump Shot   7.970

action_typeFadeaway Jump Shot     6.413

action_typeDriving Dunk Shot      6.356



```{r, eval=FALSE}

rftree2 <- train(shot_made_flag~., data=df, method = "rf", metric = 'Accuracy',trControl = control3, ntree = 200,  tuneGrid = expand.grid(.mtry = mtry))
rftree2
confusionMatrix(rftree2)
varImp(rftree2)

```


Random Forest 


23127 sample

12 predictor
2 classes: '0', '1' 

No pre-processing

Resampling: Cross-Validated (10 fold) 

Summary of sample sizes: 20814, 20815, 20814, 20814, 20814, 20814, ... 

Resampling results across tuning parameters:


mtry  Accuracy   Kappa    

1    0.5538548  0.0000000

2    0.6260212  0.1967935

3    0.6768281  0.3182533

4    0.6813682  0.3309301

5    0.6812816  0.3313894

6    0.6828814  0.3348682

7    0.6807197  0.3299289

8    0.6818437  0.3322401


9    0.6810221  0.3306640

10    0.6793360  0.3269140

11    0.6789902  0.3263171

12    0.6773033  0.3233134


Accuracy was used to select the optimal model using the largest value.

The final value used for the model was mtry = 6.

**Confusion Matrix**

(entries are percentual average cell counts across resamples)

 
********** actual

Prediction    0    1

*********0 47.6 23.9

*********1  7.8 20.7

Accuracy (average) : 0.6829

**VariableImportance**

only 20 most important variables shown (out of 118)


action_typeJump Shot            100.000

shot_distance                    52.96

loc_y                            48.555

game_date                        46.916

loc_x                            41.30

seconds_remaining                39.338

combined_shot_typeDunk           39.161

minutes_remaining                27.692

action_typeLayup Shot            25.477

action_typeDriving Layup Shot    24.759

combined_shot_typeJump Shot      22.351

action_typeRunning Jump Shot     18.399

period                           17.728

combined_shot_typeLayup          11.920

action_typeSlam Dunk Shot         7.853

action_typeDriving Dunk Shot      7.235

action_typeJump Bank Shot         7.196

action_typePullup Jump shot       6.641

action_typeTurnaround Jump Shot   6.306

action_typeFadeaway Jump Shot     5.989


```{r, eval=FALSE}
rftree3 <- train(shot_made_flag~., data=df, method = "rf", metric = 'Accuracy',trControl = control3, ntree = 400,  tuneGrid = expand.grid(.mtry = mtry))
rftree3
confusionMatrix(rftree3)
varImp(rftree3)

```

Random Forest

23127 samples

12 predictor

2 classes: '0', '1' 

No pre-processing

Resampling: Cross-Validated (10 fold) 

Summary of sample sizes: 20814, 20814, 20814, 20814, 20815, 20814, ... 

Resampling results across tuning parameters:


mtry  Accuracy   Kappa

1    0.5538548  0.0000000

2    0.6246811  0.1947518

3    0.6768275  0.3188270

4    0.6821891  0.3327854

5    0.6817998  0.3324420

6    0.6822324  0.3334287

7    0.6815402  0.3318305

8    0.6813677  0.3314107

9    0.6812808  0.3310716

10    0.6814540  0.3311948

11    0.6804166  0.3294517

12    0.6788598  0.3263128


Accuracy was used to select the optimal model using the largest value.


The final value used for the model was mtry = 6.

**ConfusionMatrix**

(entries are percentual average cell counts across resamples)
 
**********  actual 

Prediction    0    1

**********0 47.6 24.0

**********1  7.8 20.6


Accuracy (average) : 0.6822

**VariableImportance**


only 20 most important variables shown (out of 118)

action_typeJump Shot            100.000

shot_distance                    62.940

loc_y                            59.982

game_date                        53.515

loc_x                            50.488

seconds_remaining                46.968

combined_shot_typeDunk           37.425

minutes_remaining                32.774

action_typeLayup Shot            32.701

combined_shot_typeJump Shot      26.911

action_typeDriving Layup Shot    24.844

action_typeRunning Jump Shot     21.355

period                           20.135

combined_shot_typeLayup          13.849

action_typeSlam Dunk Shot        10.732

action_typeJump Bank Shot        10.226

action_typePullup Jump shot       9.577

action_typeDriving Dunk Shot      9.207

action_typeTurnaround Jump Shot   8.985

action_typeFadeaway Jump Shot     7.714






### GBM model 



```{r, eval=FALSE}

control1 <- trainControl(method='repeatedcv',number=10,repeats=3)

gbmGrid=expand.grid(interaction.depth = c(1, 3, 5), 
                    n.trees = c(50,100,150),
                    shrinkage = c(0.1,0.2,0.3),
                    n.minobsinnode = c(5,10,15))

gbmtree =train(shot_made_flag~., data=df, method="gbm", metric="Accuracy", verbose = TRUE ,trControl = control1,tuneGrid = gbmGrid)
gbmtree
confusionMatrix(gbmtree)
summary(gbmtree)


```




**Stochastic Gradient Boosting** 


23127 samples

12 predictor

2 classes: '0', '1' 


No pre-processing

Resampling: Cross-Validated (10 fold)

Summary of sample sizes: 20814, 20815, 20814, 20814, 20814, 20814, ... 

Resampling results across tuning parameters:


shrinkage  interaction.depth  n.minobsinnode  n.trees  Accuracy   Kappa 

0.1        1                   5               50      0.6783843  0.3277080
  
0.1        1                   5              100      0.6791193  0.3287339

0.1        1                   5              150      0.6809787  0.3319587

0.1        1                  10               50      0.6783843  0.3277080

0.1        1                  10              100      0.6794219  0.3292172

0.1        1                  10              150      0.6808923  0.3316635

0.1        1                  15               50      0.6783843  0.3277080

0.1        1                  15              100      0.6792490  0.3289280

0.1        1                  15              150      0.6806327  0.3311311

0.1        3                   5               50      0.6800707  0.3301796

0.1        3                   5              100      0.6814976  0.3323563

0.1        3                   5              150      0.6819733  0.3330124

0.1        3                  10               50      0.6805464  0.3311862

0.1        3                  10              100      0.6814545  0.3322189

0.1        3                  10              150      0.6807626  0.3304724

0.1        3                  15               50      0.6801138  0.3302661

0.1        3                  15              100      0.6818003  0.3328393

0.1        3                  15              150      0.6819300  0.3328977

0.1        5                   5               50      0.6808057  0.3310267

0.1        5                   5              100      0.6818436  0.3325481

0.1        5                   5              150      0.6814113  0.3315742

0.1        5                  10               50      0.6811085  0.3316535

0.1        5                  10              100      0.6822760  0.3335063

0.1        5                  10              150      0.6819301  0.3325525

0.1        5                  15               50      0.6812382  0.3319596

0.1        5                  15              100      0.6821030  0.3332083

0.1        5                  15              150      0.6811517  0.3310642

0.2        1                   5               50      0.6795518  0.3293421

0.2        1                   5              100      0.6807626  0.3311107

0.2        1                   5              150      0.6811950  0.3316042

0.2        1                  10               50      0.6792491  0.3289121

0.2        1                  10              100      0.6812382  0.3320741

0.2        1                  10              150      0.6813247  0.3318446

0.2        1                  15               50      0.6795084  0.3293512

0.2        1                  15              100      0.6808490  0.3313333

0.2        1                  15              150      0.6818004  0.3327771

0.2        3                   5               50      0.6816274  0.3325587

0.2        3                   5              100      0.6810655  0.3308830

0.2        3                   5              150      0.6795088  0.3275734

0.2        3                  10               50      0.6810653  0.3312052

0.2        3                  10              100      0.6808922  0.3306000

0.2        3                  10              150      0.6794656  0.3279443

0.2        3                  15               50      0.6805896  0.3302939

0.2        3                  15              100      0.6803734  0.3294466

0.2        3                  15              150      0.6798113  0.3288865

0.2        5                   5               50      0.6806762  0.3301535

0.2        5                   5              100      0.6782548  0.3259282

0.2        5                   5              150      0.6759197  0.3218256

0.2        5                  10               50      0.6811086  0.3309161

0.2        5                  10              100      0.6788603  0.3270648

0.2        5                  10              150      0.6753146  0.3206174

0.2        5                  15               50      0.6805896  0.3301254

0.2        5                  15              100      0.6789901  0.3271974

0.2        5                  15              150      0.6774766  0.3252442

0.3        1                   5               50      0.6806760  0.3312650

0.3        1                   5              100      0.6822759  0.3336784

0.3        1                   5              150      0.6816707  0.3321224

0.3        1                  10               50      0.6802436  0.3303614

0.3        1                  10              100      0.6815842  0.3324133

0.3        1                  10              150      0.6812814  0.3314025

0.3        1                  15               50      0.6813246  0.3324911

0.3        1                  15              100      0.6814544  0.3321186

0.3        1                  15              150      0.6814544  0.331712

0.3        3                   5               50      0.6805030  0.3298635

0.3        3                   5              100      0.6795084  0.3281496

0.3        3                   5              150      0.6762654  0.3219931

0.3        3                  10               50      0.6812383  0.3313827

0.3        3                  10              100      0.6778657  0.3250268

0.3        3                  10              150      0.6767415  0.3240266

0.3        3                  15               50      0.6816707  0.3321431

0.3        3                  15              100      0.6792930  0.3277838

0.3        3                  15              150      0.6775200  0.3250899

0.3        5                   5               50      0.6784710  0.3262163

0.3        5                   5              100      0.6748387  0.3199911

0.3        5                   5              150      0.6714659  0.3144349

0.3        5                  10               50      0.6780820  0.3251887

0.3        5                  10              100      0.6736284  0.3179590

0.3        5                  10              150      0.6715098  0.3150819

0.3        5                  15               50      0.6796818  0.3287325

0.3        5                  15              100      0.6756171  0.3219952

0.3        5                  15              150      0.6712935  0.3141821


Accuracy was used to select the optimal model using the largest value.

The final values used for the model were n.trees = 100,

interaction.depth = 5, shrinkage = 0.1 and n.minobsinnode = 10.

 
Cross-Validated (10 fold) Confusion Matrix 

(entries are percentual average cell counts across resamples)

**ConfusionMatrix**

**********  Actual

Prediction     0    1

*********0     47.6   24.0

*********1     7.8    20.6

Accuracy (average) : 0.6823


**rel.inf**

action_typeJump Shot                       44.5254897

action_typeLayup Shot                      13.9767373

game_date                                   6.52941966

combined_shot_typeDunk                      5.62550149

shot_distance                               5.2329435

loc_x                                       3.30741365

loc_y                                       3.11581554

seconds_remaining                           3.05209344

period                                      1.55793732

minutes_remaining                           1.53448513

combined_shot_typeTip Shot                  1.45944227

action_typeHook Shot                        0.90817769

action_typeRunning Jump Shot                0.82012466

action_typeDriving Layup Shot               0.66825591

action_typeJump Bank Shot                   0.62084988

action_typePullup Jump shot                 0.59640382

action_typeFadeaway Jump Shot               0.50155421

action_typeDunk Shot                        0.37300552

action_typeTurnaround Jump Shot             0.37035990

action_typeTip Shot                         0.25951266

combined_shot_typeLayup                     0.24059397

opponentNYK                                 0.23938501

season1998-99                               0.22816634

season2003-04                               0.21670095

opponentMIL                                 0.18891456

action_typeDriving Finger Roll Layup Shot   0.18710471

opponentHOU                                 0.17793387

season1999-00                               0.17051469

action_typeReverse Layup Shot               0.15882683

opponentNJN                                 0.14995526

opponentGSW                                 0.14901869

opponentORL                                 0.14712958

opponentIND                                 0.14424394

action_typeRunning Bank shot                0.14397776

opponentPHI                                 0.14293665

action_typeFinger Roll Shot                 0.13718082

opponentSAC                                 0.13234048

opponentDEN                                 0.13077240

action_typeTurnaround Bank shot             0.13050590

opponentOKC                                 0.11252563

action_typeRunning Hook Shot                0.11172618

action_typeDriving Finger Roll Shot         0.10738288

opponentWAS                                 0.10198850

opponentPHX                                 0.09955965

season1997-98                               0.09575661

season2005-06                               0.08604931

season2008-09                               0.08283710

action_typeFadeaway Bank shot               0.08258236

season2010-11                               0.07860733

season2006-07                               0.07595702

playoffs1                                   0.07559550

opponentPOR                                 0.07319416

opponentUTA                                 0.07256524

action_typeSlam Dunk Shot                   0.06432455

season2000-01                               0.06215142

opponentMIN                                 0.05673567

opponentSAS                                 0.05611338

opponentCHA                                 0.05064148

season2002-03                               0.04710334

opponentBOS                                 0.04246438

opponentTOR                                 0.03943597

action_typeFloating Jump shot               0.03685613

action_typeFinger Roll Layup Shot           0.03612042




## Make Prediction 


I used gbm whixh  n.trees = 100, interaction.depth = 5, shrinkage = 0.1 and n.minobsinnode = 10. and 
random forest which is mtry= 6 ntree=200 model to predict. 

Since the accuracy values are bigger than others.


```{r, eval=FALSE}
gbmprediction <- predict(gbmtree,test,type= "prob")
submission$shot_made_flag <- gbmprediction[,2]
write_xlsx(submission,"C:/Users/seyma/Desktop/IE425project/submission.xlsx")
 
rfprediction <- predict(rftree2,test,type= "prob")
submission$shot_made_flag <- rfprediction[,2]
write_xlsx(submission,"C:/Users/seyma/Desktop/IE425project/submission2.xlsx")
  

 
 
```









